%-------------------------------------
% LaTeX Resume for Data Science & Software Developer
% Author : Jonathan Hildenbrand
% License : MIT
%-------------------------------------

\documentclass[letterpaper,12pt]{article}[leftmargin=*]

\usepackage[empty]{fullpage}
\usepackage{enumitem}
\usepackage{ifxetex}
\ifxetex
  \usepackage{fontspec}
  \usepackage[xetex]{hyperref}
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[pdftex]{hyperref}
\fi
\usepackage{fontawesome}
\usepackage[sfdefault,light]{FiraSans}
\usepackage{anyfontsize}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{tikz}
\usetikzlibrary{tikzmark}


%-------------------------------------------------- SETTINGS HERE --------------------------------------------------
% Header settings
\def \fullname {Jonathan Hildenbrand}
\def \subtitle {Data Scientist \& Software Developer}

\def \githubicon {\faGithub}
\def \githublink {https://github.com/jonathanhild}
\def \githubtext {jonathanhild}

\def \linkedinicon {\faLinkedin}
\def \linkedinlink {https://linkedin.com/in/jonathanh3}
\def \linkedintext {jonathanh3}

\def \phoneicon {\faPhone}
\def \phonetext {+1-971-409-0695}

\def \emailicon {\faEnvelope}
\def \emaillink {mailto:jonathan.hildenbrand+resume@gmail.com}
\def \emailtext {jonathan.hildenbrand@gmail.com}

\def \locationicon {\faMapMarker}
\def \locationtext {Portland, Oregon}

\def \targeticon {\faBinoculars}
\def \targettext {Local \& Remote WFH}

\def \headertype {\doublecol} % \singlecol or \doublecol

% Misc settings
\def \entryspacing {-0pt}

\def \bulletstyle {\faAngleRight}

% Define colours
\definecolor{primary}{HTML}{000000}
\definecolor{Green}{HTML}{a0d468}
\definecolor{Red}{HTML}{ed5565}
\definecolor{Blue}{HTML}{4fc1e9}
\definecolor{Copper}{HTML}{9d8375}
\definecolor{accent}{HTML}{666666}
\definecolor{links}{HTML}{696969}
\definecolor{subtle}{HTML}{c3c3c3}

%------------------------------------------------------------------------------------------------------------------- 

% Defines to make listing easier
\def \location {\hspace{3pt}\locationicon \hspace{5pt}{\color{links}\locationtext}}
\def \target {\targeticon \hspace{3pt}{\color{links}\targettext}}
\def \phone {\phoneicon \hspace{3pt}{\color{links}{\phonetext}}}
\def \linkedin {\linkedinicon \hspace{3pt}\href{\linkedinlink}{\underline{\linkedintext}}}
\def \email {\emailicon \hspace{3pt}\href{\emaillink}{\underline{\emailtext}}}
\def \github {\githubicon \hspace{3pt}\href{\githublink}{\underline{\githubtext}}}

% Adjust margins
\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.55in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.1in}

% Define the link colours
\hypersetup{
    colorlinks=true,
    urlcolor=links,
}

% Set the margin alignment 
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-------------------------
% Custom commands

% Sections
\newcommand{\projects}[2]{\vspace{6pt}
  \colorbox{Red}{\color{white}\raggedbottom\normalsize\textbf{{#1}{\hspace{9pt}#2\hspace{4pt}}}}
}
\newcommand{\skills}[2]{\vspace{6pt}
  \colorbox{Green}{\color{white}\raggedbottom\normalsize\textbf{{#1}{\hspace{9pt}#2\hspace{4pt}}}}
}

\newcommand{\experience}[2]{\vspace{6pt}
  \colorbox{Blue}{\color{white}\raggedbottom\normalsize\textbf{{#1}{\hspace{9pt}#2\hspace{4pt}}}}
}

\newcommand{\education}[2]{\vspace{6pt}
  \colorbox{Copper}{\color{white}\raggedbottom\normalsize\textbf{{#1}{\hspace{9pt}#2\hspace{4pt}}}}
}

% Entry start and end, for spacing
\newcommand{\resumeEntryStart}{\begin{itemize}[leftmargin=2.5mm]}
\newcommand{\resumeEntryEnd}{\end{itemize}\vspace{\entryspacing}}

% Itemized list for the bullet points under an entry, if necessary
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=4.5mm]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

% Resume item
\renewcommand{\labelitemii}{\bulletstyle}
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\repo}[2]{\href{#1}{\underline{#2}}}

% Entry with title, subheading, date(s), and location
\newcommand{\resumeEntryTSDL}[4]{
  \vspace{-1pt}\item[]
    \begin{tabularx}{0.97\textwidth}{X@{\hspace{60pt}}r}
      \textbf{\color{primary}#1} & {\firabook\color{accent}\small#2} \\
      \textit{\color{accent}\small#3} & \textit{\color{accent}\small#4} \\
    \end{tabularx}\vspace{-6pt}
}

% Entry with title and date(s)
\newcommand{\resumeEntryTD}[2]{
  \vspace{-1pt}\item[]
    \begin{tabularx}{0.97\textwidth}{X@{\hspace{60pt}}r}
      \textbf{\color{primary}#1} & {\firabook\color{accent}\small#2} \\
    \end{tabularx}\vspace{-6pt}
}

% Entry for special (skills)
\newcommand{\resumeEntryS}[2]{
  \item[]
    \vspace{-1pt}
      \begin{tabular}{ p{2in} m{5.5in} }
      {\small{\textbf{#1 }}} & {\small{#2}}
      \end{tabular}\vspace{-6pt}
}

\newcommand{\tag}[1]{%
  \tikzmarknode[fill=white,fill
opacity=0,draw=subtle!60!subtle,thick,rounded corners,inner sep=0.4ex,text height=1.5ex,text depth=.25ex, text opacity=1]{test}{\small{#1}}
}

% Double column header
\newcommand{\doublecol}[6]{
  \begin{tabularx}{\textwidth}{Xr}
    {
      \begin{tabular}[c]{l}
        \fontsize{24}{34}\selectfont{\color{primary}{{\textbf{\fullname}}}} \\
        {\textit{\subtitle}} % You could add a subtitle here
      \end{tabular}
    } & {
      \begin{tabular}[c]{l@{\hspace{1.5em}}l}
        {\small#4} & {\small#1} \\
        {\small#5} & {\small#2} \\
        {\small#6} & {\small#3}
      \end{tabular}
    }
  \end{tabularx}
}

% Single column header
\newcommand{\singlecol}[6]{
  \begin{tabularx}{\textwidth}{Xr}
    {
      \begin{tabular}[b]{l}
        \fontsize{35}{45}\selectfont{\color{primary}{{\textbf{\fullname}}}} \\
        {\textit{\subtitle}} % You could add a subtitle here
      \end{tabular}
    } & {
      \begin{tabular}[c]{l}
        {\small#1} \\
        {\small#2} \\
        {\small#3} \\
        {\small#4} \\
        {\small#5} \\
        {\small#6}
      \end{tabular}
    }
  \end{tabularx}
}

\begin{document}
%-------------------------------------------------- BEGIN HERE --------------------------------------------------

%---------------------------------------------------- HEADER ----------------------------------------------------
\headertype{\github}{\linkedin}{\phone}{\location}{\target}{\email} % Set the order of items here

%-------------------------------------------------- PROJECTS --------------------------------------------------
\projects{\faFlask}{Projects}

  \resumeEntryStart
    \resumeEntryTD
      {Recommender System for Books using NLP}{\repo{https://github.com/jonathanhild/powellsbooks}{https://github.com/jonathanhild/powellsbooks}}
    \resumeItemListStart
      \resumeItem {\tag{In Process} The recommender algorithm uses NLP techniques to give recommendations based on Powell's Books' Staff Picks. This project includes a web scraping tool, SQLite database, and Streamlit web interface built in Python. \textit{This is an independent project not affiliated with Powell’s Books.}}
    \resumeItemListEnd
  \resumeEntryTD
      {GeoGuessr Maps}{\repo{https://github.com/jonathanhild/geoguessrmaps}{https://github.com/jonathanhild/geoguessrmaps}}
    \resumeItemListStart
      \resumeItem {Creating latitude/longitude coordinates sets made with Python and Google Maps API for Map Maker in \href{https://www.geoguessr.com}{\underline{GeoGuessr.com}}.}
    \resumeItemListEnd
  \resumeEntryEnd

%-------------------------------------------------- SKILLS --------------------------------------------------
\skills{\faGears}{Skills}
 \resumeEntryStart
  \resumeEntryS{Data Science \& Analysis}{\tag{Data Cleaning \& ETL}\tag{Machine Learning}\tag{Technical Writing}\tag{Documentation}\tag{Communication}\tag{Accounting}\tag{Database Design}\tag{Software Development}}
  \resumeEntryS{Programming Languages} {\tag{Python}\tag{T-SQL}\tag{Regex}\tag{HTML / CSS / JS}\tag{C / C++}\tag{VBA}}
  \resumeEntryS{Tools} {\tag{Anaconda}\tag{PostgreSQL}\tag{SQL Server}\tag{SQLite}\tag{SSMS}\tag{Git}\tag{Excel}}
  \resumeEntryS{Information Technology} {\tag{Database Admin}\tag{Ubuntu 16.04+}\tag{Windows Server Admin}\tag{Dynamics NAV}}

 \resumeEntryEnd
 
%-------------------------------------------------- EXPERIENCE --------------------------------------------------
\experience{\faPieChart}{Experience}
 \resumeEntryStart
   \resumeEntryTSDL
      {IT Specialist / Supplier Quality Specialist / Tech. Documents Coord.}{Aug 2012 -- Jan 2020}
      {Oregon Spice Company}{Portland, OR}
   \resumeItemListStart
    \resumeItem {ETL project to migrate 10+ years of ERP data to new system. Extensive use of Python scripting with regex for cleaning and load into Dynamics NAV. Required to perform data load in <12 hours for ERP transition.
}
    \resumeItem {Created linear regression model to dynamically select packaging components based on material densities. Used Python scripting to produce spreadsheets for loading into ERP system.}
    \resumeItem {Created reporting and analytics for multiple business units using Jet Reports (Excel).}
    \resumeItem {Database and server administrator for Dynamics NAV environment. Implemented backup and performance tuning workflows. Migrated from single-tier to two-tier environment for performance improvements.}
    \resumeItem {Management of all IT operations in organization. Equipment procurement with multiple vendors. Creation of IT business continuity plan.}
    \resumeItem {Built supplier grading/monitoring program in Tracegains SaaS with custom SQL scripting. Created supplier performance KPIs for organization. Managed supplier approval and communication with suppliers.}
    \resumeItem {Built Access program to create, manage, and version specifications. Connect to Syspro ERP using SQL and ODBC connectors. Built Access program to rapidly compute product traceability.}
    \resumeItem {Development of multiple new food safety and quality systems.}
    \resumeItem {Technical point of contact to customers on food safety and quality. Provided verbal and written communication to customers. Organized documentaion for rapid turn-around to customers.}
  \resumeItemListEnd
 \resumeEntryEnd

  \resumeEntryStart
    \resumeEntryTSDL
      {QA Supervisor}{Nov 2011 -- Apr 2012}
      {Bridgetown Natural Foods}{Portland, OR}
    \resumeItemListStart
      \resumeItem {Supervised 6-person QA and sanitation team.}
    \resumeItemListEnd
  \resumeEntryEnd
  
\pagebreak 

   \resumeEntryStart
    \resumeEntryTSDL
      {QA Projects Leader}{Aug 2010 -- Oct 2011}
      {Sunshine Dairy Foods}{Portland, OR, USA}
    \resumeItemListStart
      \resumeItem {Development of food safety systems and GFSI readiness.}
    \resumeItemListEnd
  \resumeEntryEnd
  
  \resumeEntryStart
    \resumeEntryTSDL
      {QA/R\&D Technician}{Apr 2008 -- Aug 2010}
      {Beaverton Foods}{Hillsboro, OR, USA}
    \resumeItemListStart
      \resumeItem {Food safety and quality assurance lab analysis.}
      \resumeItem {Product development of mustards, sauces and condiments.}
    \resumeItemListEnd
  \resumeEntryEnd
  
  \resumeEntryStart
    \resumeEntryTSDL
      {QA Projects Leader}{May 2006 -- Aug 2006}
      {Lactalis American Group}{Nampa, ID, USA}
    \resumeItemListStart
      \resumeItem {Statistical analysis of processing data to control weight variances in the mozzarella line.}
    \resumeItemListEnd
  \resumeEntryEnd
  
  \resumeEntryStart
    \resumeEntryTSDL
      {Laboratory Assistant}{May 2005 -- May 2006}
      {University of Idaho}{Moscow, ID, USA}
    \resumeItemListStart
      \resumeItem {Research project in size exclusion chromatography analysis of starch chain fractions in Teff.}
    \resumeItemListEnd
  \resumeEntryEnd

%-------------------------------------------------- EDUCATION --------------------------------------------------
\education{\faGraduationCap}{Education}

  \resumeEntryStart
    \resumeEntryTSDL
      {University of Washington}{2020 -- Present}
      {Certificate in Data Science}{Online}
    \resumeEntryTSDL
      {Dataquest.io}{2020}
      {(View) \href{https://app.dataquest.io/view_cert/G76HQZAT7X8UQNXKR3LR/}{\underline{Data Analyst in Python}}}{Online}
    \resumeEntryTSDL
      {Portland Community College}{2015}
      {Courses in Computer Science I/II}{Portland, OR}
    \resumeEntryTSDL
      {University of Idaho}{2003 -- 2007}
      {BSFS in Food Science \& Toxicology}{Portland, OR}
    
  \resumeEntryEnd
  
  \bigskip 
  
  \begin{center}
    \color{accent}\small{\textit{References are available upon request.}}
  \end{center}

\end{document}
