%-----------------------------------------------------------------------------
% LaTeX Resume for Data Science
% Author : Jonathan Hildenbrand
%-----------------------------------------------------------------------------

\documentclass[letterpaper,12pt]{article}[leftmargin=*]

\usepackage[empty]{fullpage}
\usepackage{enumitem}
\usepackage{ifxetex}
\if{xetex}
  \usepackage[T1]{fontenc}
  \usepackage[xetex]{hyperref}
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[pdftex]{hyperref}
\fi
\usepackage{fontawesome}
\usepackage[sfdefault,light]{FiraSans}
\usepackage{anyfontsize}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{tikz}
\usetikzlibrary{tikzmark}

% SETTINGS
%-----------------------------------------------------------------------------
% Header settings
\def\fullname{Jonathan Hildenbrand}

\def\githubicon{\faGithub}
\def\githublink{https://github.com/jonathanhild}
\def\githubtext{jonathanhild}

\def\linkedinicon{\faLinkedin}
\def\linkedinlink{https://linkedin.com/in/jonathanh3}
\def\linkedintext{jonathanh3}

\def\phoneicon{\faPhone}
\def\phonetext{+1-971-409-0695}

\def\emailicon{\faEnvelope}
\def\emaillink{mailto:jonathan.hildenbrand+resume@gmail.com}
\def\emailtext{jonathan.hildenbrand@gmail.com}

\def\locationicon{\faMapMarker}
\def\locationtext{Portland, Oregon}

\def\targeticon{\faBinoculars}
\def\targettext{Local \& Remote}

\def\headertype{\doublecol} % \singlecol or \doublecol

% Misc settings
\def\entryspacing{-0pt}

\def\bulletstyle{\faAngleRight}

% Define colours
\definecolor{primary}{HTML}{000000}
\definecolor{Green}{HTML}{a0d468}
\definecolor{Red}{HTML}{ed5565}
\definecolor{Blue}{HTML}{4fc1e9}
\definecolor{Copper}{HTML}{9d8375}
\definecolor{accent}{HTML}{666666}
\definecolor{links}{HTML}{696969}
\definecolor{subtle}{HTML}{c3c3c3}

% Defines to make listing easier
\def\location{\hspace{3pt}\locationicon \hspace{5pt}{\color{links}\locationtext}}
\def\target{\targeticon\hspace{3pt}{\color{links}\targettext}}
\def\phone{\phoneicon\hspace{3pt}{\color{links}{\phonetext}}}
\def\linkedin{\linkedinicon\hspace{3pt}\href{\linkedinlink}{\underline{\linkedintext}}}
\def\email{\emailicon\hspace{3pt}\href{\emaillink}{\underline{\emailtext}}}
\def\github{\githubicon\hspace{3pt}\href{\githublink}{\underline{\githubtext}}}

% Adjust margins
\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.55in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.1in}

% Define the link colours
\hypersetup{
    colorlinks=true,
    urlcolor=links,
}

% Set the margin alignment 
\raggedbottom{}
\raggedright{}
\setlength{\tabcolsep}{0in}

% COMMANDS
%-----------------------------------------------------------------------------
% Sections


\newcommand{\tag}[1]{%
  \tikzmarknode[fill=white,fill opacity=0,draw=subtle!60!subtle,thick,rounded corners,inner sep=0.4ex,text height=1.5ex,text depth=.25ex, text opacity=1]{test}{\hspace{1pt}\small{#1}\hspace{1pt}}
}

% Double column header
\newcommand{\doublecol}[6]{
  \begin{tabularx}{\textwidth}{Xr}
    {
      \begin{tabular}[c]{l}
        \fontsize{24}{34}\selectfont{\color{primary}{{\textbf{\fullname}}}}
      \end{tabular}
    } & {
      \begin{tabular}[c]{l@{\hspace{1.5em}} l}
        {\small#4} & {\small#1} \\
        {\small#5} & {\small#2} \\
        {\small#6} & {\small#3}
      \end{tabular}
    }
  \end{tabularx}
}

% START DOCUMENT
%-----------------------------------------------------------------------------
%-----------------------------------------------------------------------------
\begin{document}
\headertype{\github}{\linkedin}{\phone}{\location}{\target}{\email} % Set the order of items here

\vspace{48pt}

Dear Hiring Manager,

\vspace{24pt}

\hspace{24pt}
% My short bio
As a food scientist in the food industry, I've worked on numerous innovative projects with a focus on modern technologies. In the last 8 years, there was an explosion in the amount of data I was working with, and I started learning programming and database systems to automate significant portions of my (and others) job. I wanted a new direction in my career and became interested in how far I could push my skills and knowledge in data. I then decided in 2020 to make the switch to data analytics/science and just completed a Certificate in Data Science from the University of Washington.
% What I'm looking for
I'm currently looking to fulfill my goal of a career in data analytics.
% What is my interest in the job?
I'm interested in the Data Analyst position at Pacific Coast Fruit Company because it would be an opportunity to combine my knowledge in the food industry with data analytics.

\vspace{12pt}

\hspace{24pt}
% What kind of worker I am
I'm a highly technical, organized, detail-oriented person who delivers quality work on tight timelines. Disruptions and shifting priorities are not foreign to me. In other words it's important to be prepared for the unexpected. I've developed skills to break down projects for quicker deliverables with continuous iteration. I take consideration in the technical debt that I potentially create. It is more important to me to fulfill objectives with a goal of the right size for the right job.

\vspace{12pt}

\hspace{24pt}
% Describe technical skills relevant to the job posting
I have over 10 years experience altogether in various technologies from Excel to deep learning libraries. I've built database systems in Access to manage specification versioning. I wrote scripts in Python to convert and migrate 10 years of company data to a new ERP system. I have experience working with sales, customer service, and other non-technical team members to train them on new software, diagnose issues, and deliver the kinds of features that they need. I'm currently working on a personal project that is scraping data from over 4 million web pages and will be experimenting with natural language processing and graph network algorithms to find hidden associations in heavy metal bands. One of be main reasons I got into data analytics though is making tools for people to solve business problems, not just to write software all day. Communication, understanding, and focused on people-first is at the core of my values as a data analyst.

\vspace{12pt}

\hspace{24pt}I look forward to discussing what I can bring to the job and where I can help Pacific Coast Fruit Company grow. I'm available for interviews at any time and can start immediately. Thank you in advance for your consideration.

\vspace{24pt}

Sincerely,

\vspace{12pt}

Jonathan Hildenbrand

% END DOCUMENT
%-----------------------------------------------------------------------------
%-----------------------------------------------------------------------------
\end{document}